 \documentclass[a4paper,12pt]{report}



 \begin{document}
 
\title{\textbf{MAKERERE UNIVERSITY}\vspace{12pt} \\\large  \textbf{SCHOOL OF COMPUTING AND INFORMATION TECHNOLOGY} \\\  \textbf{DEPARTMENT OF COMPUTER SCIENCE}\vspace{12pt}\\\  \textbf{A RESEARCH REPORT ABOUT LIFE AT CAMPUS}\vspace{12pt}\\\ \textbf{BY}}

\author {\textbf{Taremwa Joab}\\\ \textbf{15/U/13099/EVE 215002968}}

\maketitle

\pagenumbering{roman}

\renewcommand{\thechapter}{\Roman{chapter}} 
\section {{\LARGE  Title}}
A research report about life at campus.
 
\section{{\LARGE Executive summery}}
The aim of this report was to get the knowledge about how data is collected and how to collect it singg different tools forexample open data kit building, collecting data and creating aggregate server. And making a report about the data collected through research. The term or statement life at campus covers only the people or students who are in different universities, the information was gathered through data collection and interview. Discoveries through this data collection and research is that most campusers enjoy the life at campus even though there are some stressing factors like couse works, reaching time for exams when you aree not yet prepared for them.
 
 \section{{\LARGE Introduction}}
Life at campus is all about how students live, their conduct and the ways of living forexample how they spend their free time like playing games, playing music, etc. and there are other ways like attending lectures and readind books, going to church. live

\section{\LARGE Methodology}
This information was collected by interviewing some students from makerere university. Some students made some remarks that it is enjoyable at the same time alot of hustling. 

\section{{\LARGE Findings/results}}
It has been found out that the life at best life ever which some one experiences in life because some one is always do to what he/she wants. it is the life of freedom ,  They spend their big portion of time in playing games, going to church, playing music and other time for books

\section{{\LARGE Conclusion}}
In conclusion, the life at campus for each student is totally different from one another due to the way they spend their time differently, those who are living the ways in which the university can not allow should change like taking alot of alcohol, smoking should change because they have side effects like causing cancer.

\begin{thebibliography}{9}

\bibitem{lamport94}
  https://lifeatcampus-168309.appspot.com

\end{thebibliography}


 \end{document}